The ANthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-09-18 paper.tex
finish section 'resolving incongruities'

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{img/corpus_ossis_pubis.png}
\caption{}\label{fig:corpus_ossis_pubis}
\end{figure}

@@

\subsection{Validation}
When transforming the input sheet to ANNOds, SMOG~\citep{smog} executes some basic validation heuristics, such as warning on undefined references.
\todo{pyshacl}

>>>>

@@

%\subsection{Validation}
%When transforming the input sheet to ANNOds, SMOG~\citep{smog} executes some basic validation heuristics, such as warning on undefined references.
%\todo{pyshacl}

\subsection{Resolving incongruities}

\begin{figure}[h]
\centering
\includegraphics[width=0.6\textwidth]{img/corpus_ossis_pubis.png}
\caption{The \emph{Corpus ossis pubis} (pubic body, see \cref{fig:corpusossispubis}) forms the proximal part of the \emph{Os pubis} and includes the anterior part of the \emph{Acetabulum} as well as the \emph{Eminentia iliopubica}, which is a small elevation on the \emph{Corpus ossis pubis}.
According to the \emph{TA} and others~\citep{ta2,schemamann,anatomylexicon2007,drake2019gray,anatomylexicon,prometheus2,anatomie}, this landmark is located in the region of the \emph{Facies symphysialis}, which is defined here as the \emph{Pars symphysialis}.
}\label{fig:corpusossispubis}
\end{figure}

The domain experts reconciled conflicting literature to arrive at a consistent and logical result, for example for the \emph{Corpus ossis pubis}, see \cref{fig:corpusossispubis}.
Since the Corpi of the \emph{Os ischii} and \emph{Os ilii} are located in the area of the \emph{Acetabulum},
it is logical to place the \emph{Corpus ossis pubis} in this region as well~\citep{graysanatomy,waldeyer,allgemeineanatomie,datacollection,romanianmandible}, thereby forming the \emph{Acetabulum} from all Corpi (\emph{Corpus ossis ilii}, \emph{Corpus ossis ischii}, and \emph{Corpus ossis pubis}).
The \emph{Pars symphysialis ossis pubis} has ventral-medially the \emph{Facies symphysialis}, which connects the paired \emph{Ossa pubes} of the pelvic bones.
In the \emph{Pars symphysialis}, the \emph{Ramus inferior ossis pubis} and \emph{Ramus superior ossis pubis} merge into each other.
This redefinition closes the resulting gap in the definition of the area between the \emph{Ramus inferior ossis pubis} and the \emph{Ramus superior ossis pubis}.
